A Study on Common Bug Fix Patterns in Rust

### 2022-10-14 sections/related.tex
added fixed to related

% say why pattern-based repair is different from search-based repair -- isn't it sufficient to refer the reader to the survey?
% Pan et al: was it manual? or not? summarize their technique and say whether what they found is similar to what we found.
The main intuition in pattern-based program repair methods is that bug fixes follow certain patterns. Thus, having a collection of common bug fix patterns is a crucial step for developing such repair tools. Pan et al.~\cite{pan2009toward} analyzed seven large-scale widely used Java projects and obtained 27 common bug fix patterns. Though they did the analysis on Java projects, their reported patterns were not specific to Java. Martinez and Monperrus~\cite{martinez2015mining,martinez2012mining} exploited the frequency of observed patterns to introduce a heuristic patch searching method. In their empirical evaluation, they concluded that choosing repair actions probabilistically (weighted by frequency) can help with reducing the search space, hence creating a more effective repair tool.

@@

We would characterize our work as the Rust version of what was done in~\cite{hanam2016discovering} and~\cite{yang2022mining}. Like~\cite{hanam2016discovering}, we used DBSCAN to cluster fixes. However, our novel program encoding approach differs from what they did. Also, like~\cite{yang2022mining}, we introduced patterns in two different categories. In our case there were general and language-specific patterns; for Rust, the language-specific patterns were related to the borrow checker (BC patterns).
% ok they didn't do our program encoding; what did they do instead?

@@

Li et al.~\cite{li2021mirchecker} present MirChecker, a fully automated bug detection framework for Rust. This framework works by carrying out static analysis on Rust's Mid-level Intermediate Representation (MIR). The tool exploits the insights obtained from observing existing bugs in Rust code bases. Using both numerical and symbolic information, the framework detects errors by using constraint solving techniques. MirChecker detected 33 new bugs, including 16 memory safety faults, across 12 Rust crates.
% how do they get the set of existing bugs?
% what do you mean by numerical information?

>>>>

The main intuition in pattern-based program repair methods is that bug fixes follow certain patterns. Thus, having a collection of common bug fix patterns is a crucial step for developing such repair tools. Pan et al.~\cite{pan2009toward} analyzed seven large-scale widely used Java projects and obtained 27 common bug fix patterns. They used a bug fix pattern extractor tool to automatically parse and detect bug patterns within the bug fix hunks with less than seven statements. They ignored larger bug fix hunks as they tended to exhibit random changes and did not have observable meaningful patterns. Though they did the analysis on Java projects, their reported patterns were not specific to Java. Martinez and Monperrus~\cite{martinez2015mining,martinez2012mining} exploited the frequency of observed patterns to introduce a heuristic patch searching method. In their empirical evaluation, they concluded that choosing repair actions probabilistically (weighted by frequency) can help with reducing the search space, hence creating a more effective repair tool.

@@

We would characterize our work as the Rust version of what was done in~\cite{hanam2016discovering} and~\cite{yang2022mining}. Like~\cite{hanam2016discovering}, we used DBSCAN to cluster fixes. However, our novel program encoding approach differs from what they did. In~\cite{hanam2016discovering}, they introduced Feature Properties table, which is a categorization for program elements. Encoding programs based on this table resulted in a order-sensitive encoding, however, it made the datapoints sparse. Moreover, like~\cite{yang2022mining}, we introduced patterns in two different categories. In our case there were general and language-specific patterns; for Rust, the language-specific patterns were related to the borrow checker (BC patterns). However, in oppose to our paper, in~\cite{yang2022mining}, they did a much more elaborate manual analysis, as in their data collection, they only collected general information about the single hunk changes (e.g. the number of variables, or arguments).

@@

Li et al.~\cite{li2021mirchecker} present MirChecker, a fully automated bug detection framework for Rust. This framework works by carrying out static analysis on Rust's Mid-level Intermediate Representation (MIR). The tool exploits the insights obtained from observing existing bugs (by studying reported CVEs) in Rust code bases. Using both numerical (e.g. integer bounds) and symbolic (e.g. modelling memory) information, the framework detects errors by using constraint solving techniques. MirChecker detected 33 new bugs, including 16 memory safety faults, across 12 Rust crates.
